---
title: "sllobs-lecture-03"
author: "Aaron Quinlan"
date: "6/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Establish our working directory
Use the `setwd()` function to establish our "Desktop" as R's working directory.

```{r}
# the following setwd() command is for OS X
setwd("~/Desktop")
```

## Download raw data file to our Desktop
Let's begin by downloading the relevant RNA-seq gene counts data for two control conditions and two experimental conditions using R's `download.file()` function. We will rename the file we download to `genecounts.fixed.tsv`

```{r}
download.file(url="https://raw.githubusercontent.com/quinlan-lab/sllobs-biostats/master/data/lecture-03/airway_scaledcounts.subset.euro.fixed.tsv",
destfile="genecounts.fixed.tsv")

```

## Import into a data frame
Now let's load the file we downloaded to our Desktop into a data frame called `gene_counts`. Specify that the file has a header which names each column and that the file uses "," as the decimal separator
```{r}
gene_counts <- read.table("genecounts.fixed.tsv", header=TRUE, dec=",")
```
